---
title: "R Notebook"
output:
  html_document:
    df_print: paged
---

```{r, message=FALSE}
rm(list=ls())
library(readxl)
library(Hmisc)
library(MASS)
library(caret)
library(regclass)
library(ISLR)
library(boot)
library(vcd)
library(pROC)
library (ROCR)
library(readxl)
```

#### Reading the data

```{r}
ass3_data <- readxl::read_excel("Assignment3HW3_Data.xlsx", sheet="Data 3")
data <- data.frame(ass3_data[,c(2, 5:8)])
colnames(data) <- c("Customer ID", "Customer_Age", "Joined", "Churned", "Avg_Spend")
head(data)
```

#### Summary of the data

```{r}
summary(data)
```

#### Running the logistic regression

```{r}
mylogit<-glm(Churned ~ Avg_Spend + Customer_Age + Joined, 
             data=data, 
             family = binomial(link="logit")
             )
```

##### Displaying the co-efficients

```{r}
summary(mylogit)
```

#### Displaying the odds ratio

```{r, message = FALSE}
oddsr=round(exp(cbind(OddsRatio=coef(mylogit),confint(mylogit))),4)
oddsr
```

#### Plotting the confusion matrix

```{r}
confmat<-confusion_matrix(mylogit) 
confmat
#Predict True/False Positive/Negative (TP,TN,FP.FN)
#the confmat shows in a different order than the slides, so re-ordering.
#oldconfmat=confmat
#oldconfmat
confmat=t(confmat) 
n_o=c(2,1,3) #new order for better comparison
confmat <- confmat[n_o,n_o]
confmat
```

#### Predicting the probabilities

```{r}
predict_prob <- predict(mylogit,
                        newdata = data,
                        type="response")
data$pred_churn = predict_prob
data$retention = 1- predict_prob
head(data)
```

#### Plotting the ROC

```{r}
roc(data$Churned,mylogit$fitted.values, plot=TRUE, legacy.axes=TRUE, percent=TRUE, xlab="FP Rate", ylab="TP Rate",print.auc=TRUE)
```

#### Calculating the evaluation metrics of the model

```{r}
TP <- confmat[1,1]
FP <- confmat[1,2]
TN <- confmat[2,2]
FN <- confmat[2,1]

precision <- TP*100/(TP+FP)
round(precision, 2)

recall <- TP*100/(TP+FN)
round(recall, 2)

F1_score <- 2*precision*recall/(precision + recall)
round(F1_score, 2)
```


#### Adding the margin

```{r}
data$margin = data$Avg_Spend * 0.5
head(data)
```

#### Calculating the CLV

```{r}
i = 0.0010728

data$clv = data$margin * (1 + i)/(1 + i - data$retention)
head(data)
```

#### Average retention rate, margin, lifetime and clv

```{r, message=FALSE}
library(dplyr)
online_cust = data %>% filter (Joined == 1)

online_avg_retention = mean(online_cust$retention)
online_avg_retention

online_avg_margin = mean(online_cust$margin)
online_avg_margin

online_avg_clv = mean(online_cust$clv)
online_avg_clv

not_online_cust = data %>% filter (Joined == 0)

not_online_avg_retention = mean(not_online_cust$retention)
not_online_avg_retention

not_online_avg_margin = mean(not_online_cust$margin)
not_online_avg_margin

not_online_avg_clv = mean(not_online_cust$clv)
not_online_avg_clv
```

#### Using t-test to get point estimate for change in retention

```{r}
online_retention <- online_cust$retention
non_online_retention <- not_online_cust$retention

var.test(online_retention,
         non_online_retention,
         alternative = "two.sided")

t.test(online_retention,
       non_online_retention,
       var.equal = TRUE,
       alternative = "less")
```

#### Using t-test to check difference in CLV for online vs not online customers

```{r}
online_clv <- online_cust$clv
non_online_clv <- not_online_cust$clv

var.test(online_clv,
         non_online_clv,
         alternative="two.sided")

t.test(online_clv,
       non_online_clv,
       var.equal = FALSE,
       alternative = "greater")
```